COG-ED Manuscript

### 2021-10-22 06_Paper/COG-ED/Manuscript.Rmd
contrasts
set orthogonal contrasts;
comment on emmeans

@@

      hypothesis1a_rmanova <- afex::aov_ez(data = h1a_data,
                                           dv = "d",
                                           id = "subject",
                                           within = "level",
                                           type = 3,
                                           include_aov = TRUE)

      # specify contrasts

      hypothesis1a_emm <- emmeans(object = hypothesis1a_rmanova$aov,
                                  specs = "level")
      hypothesis1a_contrasts <- pairs(hypothesis1a_emm)

@@

      # specify contrasts

      hypothesis1b_emm <- emmeans(object = hypothesis1b_rmanova$aov,
                                  specs = "level")
      hypothesis1b_contrasts <- pairs(hypothesis1b_emm)

@@

      # specify contrasts

@@

  # specify contrasts

  hypothesis2a_emm <- emmeans(object = hypothesis2a_rmanova$aov,
                              specs = "level")
  hypothesis2a_contrasts <- pairs(hypothesis2a_emm)

>>>>

  set_sum_contrasts()   # sets orthogonal contrasts for mixed-effects model 
                        # and rmANOVA globally in order to get meaningful Type-III tests

@@

      # calculate ANOVA
      hypothesis1a_rmanova <- afex::aov_ez(data = h1a_data,
                                           dv = "d",
                                           id = "subject",
                                           within = "level",
                                           type = 3,
                                           include_aov = TRUE)

      # obtain estimated marginal means for ANOVA model
      hypothesis1a_emm <- emmeans(object = hypothesis1a_rmanova$aov,
                                  specs = "level")
      # calculate pairwise comparisons on estimated marginal means
      hypothesis1a_contrasts <- pairs(hypothesis1a_emm)

@@

      # obtain estimated marginal means for ANOVA model
      hypothesis1b_emm <- emmeans(object = hypothesis1b_rmanova$aov,
                                  specs = "level")
      # calculate pairwise comparisons on estimated marginal means
      hypothesis1b_contrasts <- pairs(hypothesis1b_emm)

@@

      # obtain estimated marginal means for ANOVA model and
      # calculate pairwise comparisons on estimated marginal means

@@

  # obtain estimated marginal means for ANOVA model
  hypothesis2a_emm <- emmeans(object = hypothesis2a_rmanova$aov,
                              specs = "level")
  # calculate pairwise comparisons on estimated marginal means
  hypothesis2a_contrasts <- pairs(hypothesis2a_emm)
